An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-01 poly-embed-journal/poly-embed-journal.tex
A few journal revisions

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\editor{TBD}

@@

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\raf{Explain why this choice of link is not calibrated}
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\reviewer}[1]{\reviewerresponse{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

@@

\editor{Tong Zhang}

@@

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewer{Explaining why $(L, \psi)$ is not calibrated w.r.t. $0-1$ loss.}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.
